### 2022-03-25 ehoh2/ehoh2.tex
indexing

Computing bindings is the only point in the procedure where the search tree
branches and different possibilities are explored. Thus, when \ehohii{} follows
the branch indicated by the binding module, it records the state to which it
needs to return, should the followed branch be backtracked. Therese are values
of $\vn{constraints}, \vn{steps}$, and $\vn{subst}$ before the branch is followed
and the value of the \vn{branch\_iter} that points past the followed branch. The
values of \vn{branch\_iter} are either \cn{BindBegin}, which denotes that no
binding was created, intermediate values that \cn{NextBinding} uses to remember
how far through bindings it is, and \cn{BindEnd}, which indicates that all
bindings are exhausted.

@@

\ourpara{Matching} In Ehoh, the matching algorithm is mostly used inside
simplification rules such as demodulation and subsumption \cite{ss-02-brainiac}.
As these rules must be efficiently performed, using any complex matching
algorithm is not a viable option. Instead, we implemented a matching algorithm
for the pattern class of terms \cite{tn-93-patterns} to complement Ehoh's
$\lambda$-free higher-order matching algorithm \cite[Sect.~4]{section-ehoh}.
A term is a \emph{pattern} if each of its free variables either
has no arguments (as in first-order logic) or is applied to distinct De Bruijn
indices.

@@

\ourpara{Indexing} Ehoh, like other modern theorem provers, efficiently retrieves
unifiable or matchable pairs of terms using indexing data structures. To find
terms unifiable with a query term or instances of a query term it uses
\emph{fingerprint indexing} \cite{ss-12-fp-indexing}. We extended this data
structure to support (full) higher-order terms in Zipperposition
\cite[Sect.~6]{unif-section}. We used the same approach in \ehohii{},
and we extended feature vector indices \cite{ss-2013-feature-vector}
in the same way.

Ehoh uses \emph{perfect discrimination trees} \cite{mcc-92-pdts} to find
generalizations of the query term (i.e., terms of which the query term is an instance).
This data structure is a trie
that indexes terms by representing them in a serialized, flattened form.
%\begin{rep}, where each node corresponds to a symbol in a term\end{rep}.
The left branch from the root in Figure \ref{fig:pdt} shows how the first-order terms
$\cst{f}\, \cst{a} \, X$ and $\cst{f}\, \cst{a} \, \cst{a}$ are stored.
In Ehoh, this data structure is extended to support partial application
and applied variables \cite{section-ehoh}.

@@

Following the notation from the extension of perfect discrimination trees to
$\lambda$-free higher-order logic \cite{section-ehoh}, we now describe how enumeration of
generalizations is performed. To traverse the tree, \ehohii{} begins at the root
node and maintains two stacks:\ \tstack{} and \tproc{}, where \tstack{} contains the
subterms of the query term that have to be matched, and \tproc{} contains
processed terms that are used to backtrack to previous states. Initially,
\tstack{} contains the query term, the current matching substitution
$\sigma$ is empty, and the successor node is chosen among the child nodes as
follows:

>>>>

Computing bindings is the only point in the procedure where the search tree
branches and different possibilities are explored. Thus, when \ehohii{} follows
the branch indicated by the binding module, it records the state to which it
needs to return, should the followed branch be backtracked. It saves the values
of $\vn{constraints}, \vn{steps}$, and $\vn{subst}$ before the branch is followed
and the value of the \vn{branch\_iter} that points past the followed branch. The
values of \vn{branch\_iter} are either \cn{BindBegin}, which denotes that no
binding was created, intermediate values that \cn{NextBinding} uses to remember
how far through bindings it is, and \cn{BindEnd}, which indicates that all
bindings are exhausted.

@@

\subsection{Matching}

In E, the matching algorithm is mostly used inside
simplification rules such as demodulation and subsumption \cite{ss-02-brainiac}.
As these rules must be efficiently performed, using any complex matching
algorithm is not a viable option. Instead, we implemented a matching algorithm
for the pattern class of terms \cite{tn-93-patterns} to complement Ehoh's
$\lambda$-free higher-order matching algorithm (Sect.~\ref{sec:ehoh:unif-match}).
A term is a \emph{pattern} if each of its free variables either
has no arguments (as in first-order logic) or is applied to distinct De Bruijn
indices.

@@

\subsection{Indexing} E, like other modern theorem provers, efficiently retrieves
unifiable or matchable pairs of terms using indexing data structures. To find
terms unifiable with a query term or instances of a query term it uses
\emph{fingerprint indexing} \cite{ss-12-fp-indexing}. We extended this data
structure to support (full) higher-order terms in Zipperposition (Sect.~\ref{sec:unif:indexing}). 
We used the same approach in \ehohii{},
and we extended feature vector indices \cite{ss-2013-feature-vector}
in the same way.

E uses \emph{perfect discrimination trees} \cite{mcc-92-pdts} to find
generalizations of the query term (i.e., terms of which the query term is an instance).
This data structure is a trie
that indexes terms by representing them in a serialized, flattened form.
%\begin{rep}, where each node corresponds to a symbol in a term\end{rep}.
The left branch from the root in Figure \ref{fig:pdt} shows how the first-order terms
$\cst{f}\, \cst{a} \, X$ and $\cst{f}\, \cst{a} \, \cst{a}$ are stored.
In Ehoh, this data structure is extended to support partial application
and applied variables (Sect.~\ref{sec:ehoh:indexing}).

@@

\looseness=-1
Following the notation from the extension of perfect discrimination trees to
$\lambda$-free higher-order logic (Sect. \ref{sec:ehoh:indexing}), we now describe how enumeration of
generalizations is performed. To traverse the tree, \ehohii{} begins at the root
node and maintains two stacks:\ \tstack{} and \tproc{}, where \tstack{} contains the
subterms of the query term that have to be matched, and \tproc{} contains
processed terms that are used to backtrack to previous states. Initially,
\tstack{} contains the query term, the current matching substitution
$\sigma$ is empty, and the successor node is chosen among the child nodes as
follows:
